Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-23 paper/v1.0/sections/appendix_a.tex
Add urls to bib
Formatting and corrections

The deriving process of solutions for Schrödinger equation with Hamiltonian of an electron in 2DEG (Eq. \ref{eq_1}) quite similar to that followed in Refs. \cite{husmi53,dini16}. We start with expanding the Hamiltonian for two-dimentional case
\begin{equation} \label{eq_a1}
  \hat{H}_e(t) = \frac{1}{2m_e}\left[
    \left(\hat{p}_x + eBy \right)^2 +
    \left(\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right)^2
  \right],
\end{equation}
and since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$ both operators share same (simultaneous) eigenfunctions
$\frac{1}{\sqrt{L_x}}\exp(\frac{ip_x x}{\hbar})$ with $p_x = 2\pi \hbar m/L_x~,~ m \in \mathbb{Z}$.
Therefore, we re-arrange the Hamiltonian using definition of canonical momentum in $y$-direction to derive
\begin{equation} \label{eq_a2}
    \hat{H}_e(t) = \frac{1}{2m_e}\left[
      \left({p}_x + eBy \right)^2 +
      \left(-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\right)^2
    \right].
\end{equation}
We now define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 \equiv {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 \equiv {eB}/{m_e}$. This leads to a new arrangement of the Hamiltonian
\begin{equation} \label{eq_a3}
  \begin{aligned}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
      \frac{1}{2m_e}\bigg[
      -\hbar^2 \pdv[2]{\tilde{y}} & +
      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{\tilde{y}} \\
      & +
      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
      \bigg],
  \end{aligned}
\end{equation}
where we used a variable substitution $\tilde{y} = (y - y_0)$. Now we are assuming that the wave function solutions for the time-dependent Schrödinger equation of considering quantum system
\begin{equation} \label{eq_a4}
    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
\end{equation}
can present by the following form
\begin{equation} \label{eq_a5}
    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
      \frac{ip_x x}{\hbar} +
      \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
    \bigg) \vartheta(\tilde{y},t),
\end{equation}
where $\vartheta(\tilde{y},t)$ is a function that need to be found to satisfy the following property
\begin{equation} \label{eq_a6}
    \bigg[
    \frac{m_e \omega_0^2}{2}\tilde{y}^2
    - {eE\tilde{y}}\sin(\omega t)
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}}
    - i \hbar \dv{t}
    \bigg]
    \vartheta(\tilde{y},t) = 0.
\end{equation}
If we turn off the strong dressing field ($E=0$), this equation leads to simple harmonic oscillator Hamiltonian
\begin{equation} \label{eq_a7}
     i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    \bigg]
    \vartheta(\tilde{y},t).
\end{equation}
It is important to notice that we can identify the $S(t) \equiv eE\sin(\omega t)$ part as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis.
\begin{equation} \label{eq_a8}
  \begin{aligned}
    i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    - \tilde{y}S(t)]
    \bigg]
    \vartheta(\tilde{y},t).
  \end{aligned}
\end{equation}

This system can be exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husmi53} as follows. We introduce a time dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform following unitary transformation
\begin{equation} \label{eq_a9}
    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t),
\end{equation}
and this yields
\begin{equation} \label{eq_a10}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   &=
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 y'^2 \\
        & +
        \Big[
            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
        \Big]y' \\
        &
        +
        \Big[
            - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
        \Big]
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Then we can restrict our $\zeta(t)$ function such that
\begin{equation} \label{eq_a11}
  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
\end{equation}
and that leads to
\begin{equation} \label{eq_a12}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}} &
        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \\
        &
        - L(\zeta,\dot{\zeta},t)
    \bigg]\varphi(y',t),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_a13}
  L(\zeta,\dot{\zeta},t) \equiv \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
\end{equation}
is the Lagrangian of a classical driven oscillator. To proceed further, another unitary transform can be introduced as follows
\begin{equation} \label{eq_a14}
    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t),
\end{equation}
and subtitling Eq.~(\ref{eq_a14}) back in Eq.~(\ref{eq_a12}) yields
\begin{equation} \label{eq_a15}
    i \hbar \pdv{t} \chi(y',t)  =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 {y'}^2
    \bigg] \chi(y',t).
\end{equation}
This is the well known Schrödinger equation of the quantum harmonic oscillator.
This allows us to identify with the well-known eigenfunctions \cite{griffiths18,shankar94}
\begin{equation} \label{eq_a16}
  \chi_n(y) \equiv
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y) \quad \text{with}
  \quad
  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
\end{equation}
which are propositional to the Hermite polynomials $\mathcal{H}_n$, with eigenvalues
\begin{equation} \label{eq_a17}
  \varepsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
  ~,~
  n \in \mathbb{Z}^{+}_0.
\end{equation}
Therefore, we can identify the solutions of Eq.~(\ref{eq_a8}) as
\begin{equation} \label{eq_a18}
  \begin{aligned}
    \vartheta_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
     \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \varepsilon_nt +
    m_e\dot{\zeta(t)}\big(\tilde{y}-\zeta(t)\big) \\
     & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}
The set $\{\chi_n(x)\}$ functions forms a complete set and thus any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of solutions derived in Eq.~(\ref{eq_a18}).

Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we can derive the solution for Eq.~(\ref{eq_a11})
\begin{equation} \label{eq_a19}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
\end{equation}
Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we can obtain the set of wave functions with two different quantum number ($n$,$m$) that satisfy the Schrödinger equation Eq.~(\ref{eq_a4})
\begin{equation} \label{eq_a20}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  = \frac{1}{\sqrt{L_x}}
    \chi_n\left[y - y_0 - \zeta(t)\right]
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \varepsilon_nt \\
    &
    + p_x x + \frac{eE(y - y_0)}{\omega}\cos(\omega t)+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]\\
    & +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}

>>>>

The deriving process of solutions for time dependent Schrödinger equation with the Hamiltonian of our system (Eq. \ref{eq_1}) quite similar to that followed in Refs. \cite{husimi53,dini16}. We start with expanding the Hamiltonian for two-dimentional case
\begin{equation} \label{eq_a1}
  \hat{H}_e(t) = \frac{1}{2m_e}\left[
    \left[\hat{p}_x + eBy \right]^2 +
    \left[\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right]^2
  \right],
\end{equation}
and since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both operators share same (simultaneous) eigenfunctions
$\frac{1}{\sqrt{L_x}}\exp(\frac{ip_x x}{\hbar})$ with $p_x = 2\pi \hbar m/L_x~,~ m \in \mathbb{Z}$.
Therefore, we re-arrange the Hamiltonian using definition of canonical momentum in $y$-direction to derive
\begin{equation} \label{eq_a2}
    \hat{H}_e(t) = \frac{1}{2m_e}\left[
      \left[{p}_x + eBy \right]^2 +
      \left[-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\right]^2
    \right].
\end{equation}
We now define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 \equiv {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 \equiv {eB}/{m_e}$. This leads to a new arrangement of the Hamiltonian
\begin{equation} \label{eq_a3}
  \begin{aligned}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
      \frac{1}{2m_e}\bigg[
      -\hbar^2 \pdv[2]{\tilde{y}} & +
      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{\tilde{y}} \\
      & +
      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
      \bigg],
  \end{aligned}
\end{equation}
where we used a variable substitution $\tilde{y} = (y - y_0)$. Now we assume that the wave function solutions for the time-dependent Schrödinger equation of considering quantum system
\begin{equation} \label{eq_a4}
    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
\end{equation}
can present by the following form
\begin{equation} \label{eq_a5}
    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
      \frac{ip_x x}{\hbar} +
      \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
    \bigg) \vartheta(\tilde{y},t),
\end{equation}
where $\vartheta(\tilde{y},t)$ is a function that satisfy the following property
\begin{equation} \label{eq_a6}
    \bigg[
    \frac{m_e \omega_0^2}{2}\tilde{y}^2
    - {eE\tilde{y}}\sin(\omega t)
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}}
    - i \hbar \dv{t}
    \bigg]
    \vartheta(\tilde{y},t) = 0.
\end{equation}
If we turn off the strong dressing field ($E=0$), this equation leads to simple harmonic oscillator Hamiltonian
\begin{equation} \label{eq_a7}
     i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    \bigg]
    \vartheta(\tilde{y},t).
\end{equation}
It is important to notice that we can identify the $S(t) \equiv eE\sin(\omega t)$ part as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis
\begin{equation} \label{eq_a8}
  \begin{aligned}
    i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    - \tilde{y}S(t)]
    \bigg]
    \vartheta(\tilde{y},t).
  \end{aligned}
\end{equation}

This system can be exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53} as follows. We introduce a time dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform following unitary transformation
\begin{equation} \label{eq_a9}
    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t),
\end{equation}
and this yields
\begin{equation} \label{eq_a10}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   &=
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 y'^2 \\
        & +
        \Big[
            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
        \Big]y' \\
        &
        +
        \Big[
            - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
        \Big]
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Then we can restrict our $\zeta(t)$ function such that
\begin{equation} \label{eq_a11}
  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
\end{equation}
and that leads to
\begin{equation} \label{eq_a12}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}} &
        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \\
        &
        - L(\zeta,\dot{\zeta},t)
    \bigg]\varphi(y',t),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_a13}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
\end{equation}
is the Lagrangian of a classical driven oscillator. To proceed further, another unitary transform can be introduced as follows
\begin{equation} \label{eq_a14}
    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t),
\end{equation}
and subtitling Eq.~(\ref{eq_a14}) back in Eq.~(\ref{eq_a12}) yields
\begin{equation} \label{eq_a15}
    i \hbar \pdv{t} \chi(y',t)  =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 {y'}^2
    \bigg] \chi(y',t).
\end{equation}
This is the well known Schrödinger equation of the quantum harmonic oscillator.
This allows us to identify with the well known eigenfunctions \cite{griffiths18,shankar94}
\begin{equation} \label{eq_a16}
  \chi_n(y) =
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y) \quad \text{with}
  \quad
  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
\end{equation}
which are propositional to the Hermite polynomials $\mathcal{H}_n$, with eigenvalues
\begin{equation} \label{eq_a17}
  \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
  ~,~
  n \in \mathbb{Z}^{+}_0.
\end{equation}
Therefore, we can identify the solutions of Eq.~(\ref{eq_a8}) as
\begin{equation} \label{eq_a18}
  \begin{aligned}
    \vartheta_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
     \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \epsilon_nt +
    m_e\dot{\zeta(t)}\big[\tilde{y}-\zeta(t)\big] \\
     & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}
Since set $\{\chi_n(x)\}$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of solutions derived in Eq.~(\ref{eq_a18}).

Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we can derive the solution for Eq.~(\ref{eq_a11}):
\begin{equation} \label{eq_a19}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
\end{equation}
Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we can obtain the set of wave functions with two different quantum number ($n$,$m$) that satisfy the time dependent Schrödinger equation Eq.~(\ref{eq_a4}) as follows
\begin{equation} \label{eq_a20}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  = \frac{1}{\sqrt{L_x}}
    \chi_n\left(y - y_0 - \zeta(t)\right)
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \epsilon_nt \\
    &
    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]\\
    & +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}

### 2021-07-23 paper/v1.0/sections/appendix_b.tex
Formatting and corrections

First define the time integral of Lagrangian of the classical oscillator given in Eq.~(\ref{eq_5}), over a $T=2\pi/\omega$ period as
\begin{equation} \label{eq_b1}
  \Delta_{\varepsilon} \equiv \frac{1}{T} \int_0^T dt' \; L(\zeta,\dot{\zeta},t'),
\end{equation}
and after performing the integral using Eq.~(\ref{eq_4}), we can obtain more simplified result:
\begin{equation} \label{eq_b2}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)}.
\end{equation}
Next define another parameter
\begin{equation} \label{eq_b3}
  \xi \equiv
  \int_0^t dt' \; L(\zeta,\dot{\zeta},t') -
  \Delta_{\varepsilon} t,
\end{equation}
and after simplifying, this leads to
\begin{equation} \label{eq_b4}
  \xi =
  \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t),
\end{equation}
which is a periodic function in time with $2\omega$ frequency. Now using these  parameters we can factorize the wave function Eq.~(\ref{eq_2}) as linearly time dependent part and periodic time dependent part as follows
\begin{equation} \label{eq_b5}
  \begin{aligned}
    \psi_{\alpha}&(x,y,t)  =
    \exp(\frac{i}{\hbar}\qty[-\varepsilon_nt + \Delta_{\varepsilon} t ])
    \frac{1}{\sqrt{L_x}} \chi_n\big(y - y_0 - \zeta(t)\big)
    \\
    & \times
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x +
     \frac{eEy}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta(t)}\big[y-\zeta(t)\big]
     + \int_0^{t}dt'L(\zeta,\dot{\zeta},t') - \Delta_{\varepsilon} t  \bigg]
     \bigg),
  \end{aligned}
\end{equation}
and this leads to separate linear time dependent phase component as the quasienergies
\begin{equation} \label{eq_b6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
while rest of the components as time-periodic Floquet modes
\begin{equation} \label{eq_b7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) \equiv &
    \frac{1}{\sqrt{L_x}} \chi_{n}\left[y - y_0 - \zeta(t)\right]
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x \\
     & +
     \frac{eE(y - y_0)}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg).
  \end{aligned}
\end{equation}

@@

To write the Floquet modes in momentum space, we perform continuous Fourier transform over the considering confined space $A=L_xL_y$ for Eq.~(\ref{eq_7}):
\begin{equation} \label{eq_b8}
  \begin{aligned}
    \phi_{n,m}&(k_x,k_y,t) \\
    & =
    \exp(
     \frac{-i\gamma(t)}{\hbar}
     y_0)
    \exp(\frac{-i}{\hbar}
    \qty[
    m_e \dot{\zeta}(t) \zeta(t) - \xi
    ])\\
    & \times
    \int_{-L_y/2}^{L_y/2} dy\; \exp(-i\qty[k_y - \gamma(t)]y)
    \chi_{n}\qty[y - \mu(t)] \\
     & \times
     \frac{1}{\sqrt{L_x}}
     \int_{-L_x/2}^{L_x/2} dx\;
     \exp(-ik_x x)
     \exp( \frac{i p_x }{\hbar}x ),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_b9}
  \mu(t) \equiv \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0
  \quad,\quad
  \gamma(t) \equiv
  \frac{eE\omega_0^2\cos(\omega t)}{\hbar\omega(\omega_0^2 - \omega^2)}.
\end{equation}
Next using the identity \cite{bruus04}
\begin{equation} \label{eq_b10}
  \int_{L_x} dx\;
  \exp( -ik_x x + \frac{i p_x }{\hbar}x ) =
  L_x \delta_{k_x,\frac{p_x}{\hbar}},
\end{equation}
we can derive
\begin{equation} \label{eq_b11}
  \begin{aligned}
    \phi_{n,m}&(k_x,k_y,t)  =
    \Phi_{n,m}(k_y,t)
    \delta_{k_x,\frac{p_x}{\hbar}}\\
    & \times
    \exp(
     \frac{-i\gamma(t)}{\hbar}
     y_0)
    \exp(\frac{-i}{\hbar}
    \qty[
    m_e \dot{\zeta}(t) \zeta(t) - \xi
    ]).
  \end{aligned}
\end{equation}
Here we defined $\Phi_{n,m}(k_y,t)$ as
\begin{equation} \label{eq_b12}
  \begin{aligned}
    \Phi_{n,m}(k_y,t) \equiv
    \sqrt{L_x}
    \int_{-L_y/2}^{L_y/2} dy\; &
    \chi_{n}\qty[y - \mu(t)] \\
    & \times
    \exp(
      -i\qty[k_y - \gamma(t)]
      y).
  \end{aligned}
\end{equation}
Substituting $  {k'_y} = k_y -\gamma(t)$ and $y' = y -\mu(t)$ and assuming that size of the 2DEG sample in $y$-direction is large ($L_y \rightarrow \infty$), we can obtain
\begin{equation} \label{eq_b13}
  \Phi_{n,m}({k'_y} ,t) =
  {\sqrt{L_x}} e^{-i {k'_y}\mu}
  \int_{-\infty}^{\infty} dy'\;
  \chi_{n}\qty(y')
  \exp(-i{k'_y} y').
\end{equation}
We can identify that the integral represents the Fourier transform of $\{\chi_n\}$ functions and using the symmetric conditions \cite{celeghini21} for the Fourier transform of Gauss-Hermite functions $\theta_n(x)$:
\begin{equation} \label{eq_b14}
  \mathcal{FT}[\theta_n(\kappa x),x,k] = \frac{i^n}{|\kappa|}\theta_n(k/\kappa),
\end{equation}
Eq.~(\ref{eq_b13}) can be simplified as
\begin{equation} \label{eq_b15}
  \Phi_{n,m}({k'_y} ,t) =
    \sqrt{L_x}e^{-i {k'_y}\mu}
    \tilde{\chi}_{n}\qty({k'_y}),
\end{equation}
with
\begin{equation} \label{eq_b16}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{\alpha} \qty(\frac{k}{\kappa}).
\end{equation}
Substitute Eq.~(\ref{eq_b15}) back in Eq.~(\ref{eq_b11}) and this leads to
\begin{equation} \label{eq_b17}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + \frac{\hbar k_x}{eB}]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_b18}
  b \equiv
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad
  d \equiv
 \frac{eE}{m_e(\omega_0^2 - \omega^2)},
\end{equation}
and it is necessary to notice that $k_x$ is quantized with $k_x = 2\pi m/L_x ~,~ m \in \mathbb{Z}$.

>>>>

First define the time integral of Lagrangian of the classical oscillator given in Eq.~(\ref{eq_5}), over a $T=2\pi/\omega$ period as
\begin{equation} \label{eq_b1}
  \Delta_{\varepsilon} = \frac{1}{T} \int_0^T dt' \; L(\zeta,\dot{\zeta},t'),
\end{equation}
and after performing the integral using Eq.~(\ref{eq_4}), we can obtain more simplified result:
\begin{equation} \label{eq_b2}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)}.
\end{equation}
Next define another parameter
\begin{equation} \label{eq_b3}
  \xi =
  \int_0^t dt' \; L(\zeta,\dot{\zeta},t') -
  \Delta_{\varepsilon} t,
\end{equation}
and after simplifying, this leads to
\begin{equation} \label{eq_b4}
  \xi =
  \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t),
\end{equation}
which is a periodic function in time with $2\omega$ frequency. Now using these  parameters we can factorize the wave function Eq.~(\ref{eq_2}) as linearly time dependent part and periodic time dependent part as follows
\begin{equation} \label{eq_b5}
  \begin{aligned}
    \psi_{\alpha}&(x,y,t)  =
    \exp(\frac{i}{\hbar}\qty[-\epsilon_nt + \Delta_{\varepsilon} t ])
    \frac{1}{\sqrt{L_x}} \chi_n\big(y - y_0 - \zeta(t)\big)
    \\
    & \times
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x +
     \frac{eEy}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta(t)}\big[y-\zeta(t)\big]
     + \int_0^{t}dt'L(\zeta,\dot{\zeta},t') - \Delta_{\varepsilon} t  \bigg]
     \bigg),
  \end{aligned}
\end{equation}
and this leads to separate linear time dependent phase component as the quasienergies
\begin{equation} \label{eq_b6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
while rest of the components as time-periodic Floquet modes
\begin{equation} \label{eq_b7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) \equiv &
    \frac{1}{\sqrt{L_x}} \chi_{n}\left(y - y_0 - \zeta(t)\right)
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x \\
     & +
     \frac{eE[y - y_0]}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg).
  \end{aligned}
\end{equation}

@@

To write the Floquet modes in momentum space, we perform continuous Fourier transform over the considering confined space $A=L_xL_y$ on the Floquet modes given in Eq.~(\ref{eq_7}):
\begin{equation} \label{eq_b8}
  \begin{aligned}
    \phi_{n,m}&(k_x,k_y,t) \\
    & =
    \exp(
     \frac{-i\gamma(t)}{\hbar}
     y_0)
    \exp(\frac{-i}{\hbar}
    \qty[
    m_e \dot{\zeta}(t) \zeta(t) - \xi
    ])\\
    & \times
    \int_{-L_y/2}^{L_y/2} dy\; \exp(-i\qty[k_y - \gamma(t)]y)
    \chi_{n}\qty[y - \mu(t)] \\
     & \times
     \frac{1}{\sqrt{L_x}}
     \int_{-L_x/2}^{L_x/2} dx\;
     \exp(-ik_x x)
     \exp( \frac{i p_x }{\hbar}x ),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_b9}
  \mu(t) = \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0
  \quad,\quad
  \gamma(t) =
  \frac{eE\omega_0^2\cos(\omega t)}{\hbar\omega(\omega_0^2 - \omega^2)}.
\end{equation}
Next using the Fourier transform identity \cite{bruus04}
\begin{equation} \label{eq_b10}
  \int_{L_x} dx\;
  \exp( -ik_x x + \frac{i p_x }{\hbar}x ) =
  L_x \delta_{k_x,\frac{p_x}{\hbar}},
\end{equation}
we can derive
\begin{equation} \label{eq_b11}
  \begin{aligned}
    \phi_{n,m}&(k_x,k_y,t)  =
    \Phi_{n,m}(k_y,t)
    \delta_{k_x,\frac{p_x}{\hbar}}\\
    & \times
    \exp(
     \frac{-i\gamma(t)}{\hbar}
     y_0)
    \exp(\frac{-i}{\hbar}
    \qty[
    m_e \dot{\zeta}(t) \zeta(t) - \xi
    ]).
  \end{aligned}
\end{equation}
Here we defined $\Phi_{n,m}(k_y,t)$ as
\begin{equation} \label{eq_b12}
  \begin{aligned}
    \Phi_{n,m}(k_y,t) =
    \sqrt{L_x}
    \int_{-L_y/2}^{L_y/2} dy\; &
    \chi_{n}\qty[y - \mu(t)] \\
    & \times
    \exp(
      -i\qty[k_y - \gamma(t)]
      y).
  \end{aligned}
\end{equation}
Substituting $  {k'_y} = k_y -\gamma(t)$ and $y' = y -\mu(t)$ and assuming that size of the 2DEG sample in $y$-direction is considerably large ($L_y \rightarrow \infty$), we can obtain
\begin{equation} \label{eq_b13}
  \Phi_{n,m}({k'_y} ,t) =
  {\sqrt{L_x}} e^{-i {k'_y}\mu}
  \int_{-\infty}^{\infty} dy'\;
  \chi_{n}\qty(y')
  \exp(-i{k'_y} y').
\end{equation}
We can identify that the integral represents the Fourier transform of $\{\chi_n\}$ functions and using the symmetric conditions \cite{celeghini21} for the Fourier transform of Gauss-Hermite functions $\theta_n(x)$:
\begin{equation} \label{eq_b14}
  \mathcal{FT}[\theta_n(\kappa x),x,k] = \frac{i^n}{|\kappa|}\theta_n(k/\kappa),
\end{equation}
Eq.~(\ref{eq_b13}) can be simplified as
\begin{equation} \label{eq_b15}
  \Phi_{n,m}({k'_y} ,t) =
    \sqrt{L_x}e^{-i {k'_y}\mu}
    \tilde{\chi}_{n}\qty({k'_y}),
\end{equation}
with
\begin{equation} \label{eq_b16}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{\alpha} \qty(\frac{k}{\kappa}).
\end{equation}
Substitute Eq.~(\ref{eq_b15}) back in Eq.~(\ref{eq_b11}) and this leads to
\begin{equation} \label{eq_b17}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + \frac{\hbar k_x}{eB}]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_b18}
  b \equiv
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad
  d \equiv
 \frac{eE}{m_e(\omega_0^2 - \omega^2)},
\end{equation}
and it is necessary to notice that $k_x$ is quantized with $k_x = 2\pi m/L_x ~,~ m \in \mathbb{Z}$.
